---
title: "All 25 Cities Italy"
author: "Laura Albrecht"
date: "8/6/2020"
output:
  pdf_document: default
  html_document: default
---

Create GAM models for all 25 cities in Italy as well as all of Italy combined.

```{r echo = FALSE, message = FALSE, warning = FALSE}
source("ReadAllData1.R")
library(mgcv)
#all of italy
italy_25gam <- gam(log(mean)~ 
                    s(home, k = 5)+s(pm25, k = 5)+s(med_temp, k = 5)+s(med_hum, k = 5), data = italy_25, family = gaussian)

plot(italy_25gam,scale=0,se=2, shade=TRUE,pages=1, scheme = 2,main = "25 Cities in Italy")
summary(italy_25gam)
gam.check(italy_25gam)

#all of italy including city
#italy_25f <- italy_25
#italy_25f$city_name <- as.factor(italy_25$city_name)

#italy_25gam <- gam(log(mean)~ 
#                    s(home, k = 5)+s(pm25, k = 5)+s(med_temp, k = 5)+s(med_hum, k = 5)+city_name, data = italy_25f, family = gaussian)

#plot(italy_25gam,scale=0,se=2, shade=TRUE,pages=1, scheme = 2,main = "25 Cities in Italy")
#summary(italy_25gam)


```

```{r message = FALSE, warning = FALSE, echo = FALSE}
library(mgcv)
#loop through and save gams
for(city in city_names){
  assign( paste(city,"_gam", sep = ""), gam(log(mean)~ 
                    s(home)+s(pm25, k = 5)+s(med_temp, k = 6)+s(med_hum, k = 6), data = italy_25[italy_25$city_name == city,], family = gaussian))}

#loop through and plot gams
for(city in city_names){
  plot(get(paste(city, "_gam", sep = "")),scale=0,se=2, shade=TRUE,pages=1, scheme = 2, main = city)
}

#for(city in city_names){
#  summary(get(paste(city, "_gam", sep = "")))
#}
 # summary(temp.gamM1)
 # gam.check(temp.gamM1)


```

```{r include = FALSE}
#trying with lapply

my_list <- lapply(city_names, function(x){
  summary(gam(log(mean)~ s(home)+s(pm25, k = 5)+s(med_temp, k = 6)+s(med_hum, k = 6), data = italy_25[italy_25$city_name == x,], family = gaussian))
})
```

This gratia package makes nice gam plots based off of ggplot. Have a lot of things you can customize too. Might be nice to use in presentaitons, etc
```{r echo = FALSE, warning = FALSE, message = FALSE}
#plot from my list
library(gratia)

my_gam <- gam(log(mean)~ s(home)+s(pm25, k = 5)+s(med_temp, k = 6)+s(med_hum, k = 6), data = italy_25[italy_25$city_name=="Alessandria",], family = gaussian)

#use gratia package for plotting 
draw(my_gam)
```

```{r include = FALSE}
my_big_gam <- gam(log(mean)~ s(home)+s(pm25)+s(med_temp)+s(med_hum)+s(no2)+s(o3) +ti(med_temp, med_hum)+ti(pm25, no2) + ti(pm25, o3)+ti(pm25, med_temp), data = italy_25, family = gaussian)
draw(my_big_gam)
summary(my_big_gam)
```
Plot of all R(t) curves and all infections
```{r echo = FALSE}
#plot all R(t) curves
library(ggplot2)
ggplot(italy_25, aes(date, mean, color = city_name))+geom_line()

#plot infections curve
ggplot(italy_25, aes(date, infections, color = city_name))+geom_line()
```

##What exactly is the "infections" column in the data? It's very smooth

Here I performed curve registration which essentially centers all of the curves so the peaks occur at the same time
```{r echo = FALSE}
#data registration
ind <- italy_25 %>% group_by(city_name) %>% summarise(which.max(infections))

library(zoo)
italy_25$day_num1 <- italy_25$day_num

for(i in 1:length(ind$city_name)){
italy_25[italy_25$city_name == ind$city_name[i],]$day_num1 <- italy_25[italy_25$city_name == ind$city_name[i],]$day_num - ind$`which.max(infections)`[i]
}

italy_25$Ave7Daily <- NA
italy_25$Ave7Daily[1:3744] <- rollmean(italy_25$Daily, 7)

#ggplot(italy_25[1:3744,], aes(day_num1, Ave7Daily, color = city_name))+geom_line()
italy_25$day_num2 <- italy_25$day_num1 - 54

ggplot(italy_25, aes(day_num2, infections, color = city_name))+geom_line()+labs(x= "Number of Days Since Peak", y = "Infections", title = "Centered Infections")
```

```{r echo = FALSE, include = FALSE}
my_gam <- gam(infections~ s(home)+s(pm25)+s(med_temp)+s(med_hum)+s(day_num1), data = italy_25, family = gaussian)
draw(my_gam)
```

